Deciding to Disclose

### 2015-07-06 Results.tex
Finally fixed the tables

\begin{figure}
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/honesty_sharing}
\end{adjustbox}
\caption{Impact of social learning on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
\label{fig:honest_sharing}
\end{figure}

@@

\begin{figure}[h]
\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/sharing_emulated_simulated}\end{adjustbox}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules}
\label{fig:outcome_plots}
\end{figure}

@@

\begin{figure}[h]
\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
\label{fig:emulated_sharing_iqr}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
\label{fig:emulated_payoff_group_iqr}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=119mm]{figures/honesty_sharing}
\caption{Impact of social learning on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
\label{fig:honest_sharing}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=119mm]{figures/sharing_emulated_simulated}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules}
\label{fig:outcome_plots}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=119mm]{figures/unfixed_emu_sig_iqr}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
\label{fig:emulated_sharing_iqr}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=119mm]{figures/unfixed_emu_payoff_honesty_group_iqr}
\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
\label{fig:emulated_payoff_group_iqr}
\end{figure}

### 2015-07-06 agent_models.tex
More trimming
Finally fixed the tables

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

@@

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability density function takes the form -

\begin{equation}
D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
\end{equation}

where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).

The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff becomes
simply -

@@

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), so
that the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

>>>>

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

@@

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. 
The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff is
simply -

@@

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\). Hence,
the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.
